Global patterns of forest autotrophic carbon fluxes

### 2020-05-05 manuscript/manuscript draft.Rmd
knit in fixed figure, worked on allocation
#69 , #71

We found little evidence that allocation between fluxes varied substantially with latitude or climate (Fig. S3). Of the 7 FACF ratios regressed against latitude and three climate variables (MAT, MAP, temperature seasonality), there were only five signficant relationships, all with $R^2 \le 0.4$ (Fig. S3). Specifically, the proportion of NPP allocated to $ANPP_{foliage}$ decreased with latitude ($R^2=0.32$) and increased with MAT ($R^2=0.37$), and the proportion of $NPP$ allocated aboveground ($ANPP$) decreased weakly with latitude ($R^2=0.11$) and temperature seasonality ($R^2=0.17$), while increasing with MAT ($R^2=0.11$).  There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.

@@

*reworking the above paragraph:*
We show that FACF are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple FACF varies little with respect to climate along a tropical elevational gradient [@malhi_variation_2017], 
but contrasts with observed variation in allocation along gradients of elevation [@moser_elevation_2011] 
- @gill_belowground_2016 ?
- (others in list below?)
Several trends in allocation--or lack thereof--warrant discussion.
1. CUE
2. We found a slight tendency for warmer sites to have higher aboveground allocation (Fig. S3). This is consistent with:
- [@hofhansl_new_2015] (**verify**) 
- @moser_elevation_2011 (tropical elevation gradient)
- Chen et al. 2019 (doi: 10.1111/ele.13193) - find lower partitioning belowground at higher productivity (fine root NPP scales against ANPP_foliage with a slope of ~ 0.8)
- @gill_belowground_2016
- @litton_carbon_2007 - (verify)

>>>>

There was little evidence of substantial variation in C allocation across latitude or climate (Fig. S3). Of the 7 FACF ratios regressed against latitude and three climate variables (MAT, MAP, temperature seasonality), there were only five signficant relationships, all with $R^2 \le 0.4$ (Fig. S3). Specifically, the proportion of NPP allocated to $ANPP_{foliage}$ decreased with latitude ($R^2=0.32$) and increased with MAT ($R^2=0.37$), and the proportion of $NPP$ allocated aboveground ($ANPP$) decreased weakly with latitude ($R^2=0.11$) and temperature seasonality ($R^2=0.17$), while increasing with MAT ($R^2=0.11$).  The remaining 23 relationships examined were non-significant.

@@

*reworking the above paragraph:*
We show that FACF are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple FACF varies little with respect to climate along a steep tropical elevational gradient [@malhi_variation_2017; but see @moser_elevation_2011], 
and is not surprising given that trees face some universal constraints in carbon allocation (**REFS**). 
The one trend in allocation that emerged from our analysis was a tendency for greater C allocation aboveground--and to foliage in particular--in warm tropical climates (Fig. S3). This is consistent with observations of increasing allocation to roots with declining temperature across a tropical elevational gradient [@moser_elevation_201],   
- [@hofhansl_new_2015] (**verify**) 
- Chen et al. 2019 (doi: 10.1111/ele.13193) - find lower partitioning belowground at higher productivity (fine root NPP scales against ANPP_foliage with a slope of ~ 0.8)
- @gill_belowground_2016
- @litton_carbon_2007 - (verify)
One previously hypothesized trend that was not supported by our analysis was that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to (mostly younger) extratropical forests [@delucia_forest_2007; @malhi_productivity_2012; @anderson-teixeira_carbon_2016]. Limiting the analysis to mature forests, our analysis shows no such trend (Fig. S3), suggesting that the relatively low $CUE$ of intact tropical forests is more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age [@delucia_forest_2007; @collalti_is_2019], but appears to be roughly independent of $GPP$ [@litton_carbon_2007].
